---
title: "Intervention Analysis"
author: "Gustavo Reyes"
date: "12/10/2020"
output:
  pdf_document: default
  html_document: default
---
```{r}
#Intervention Analysis for Washing and Wraaping Fruit.

```

```{r}
#Setting Working Directory
#setwd("C:/Users/gareyes3/Documents/GitHub/Share-Table-QMRA/R") 
setwd("G:/Share Table QMRA/Share-Table-QMRA/R")
```

```{r}
#Opening Libary and Inputs
source("Util_Library.R")
```

Scenario where washing is on and wrapping is off
```{r}
#Inputs and Source Files
# Source Files ------------------------------------------------------------
start_time<-Sys.time()

#Inputs
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

#Changing Inputs for Washing on, Wraaping off. 
  #Washing Between Services
  Wash_Between_Services<-0
  #Wash Selection Table Fruit
  Wash_Selection_YN_Fr<-1
  #Wash Share Table Items
  Wash_ST_YN_Fr<-1
  
#Changing Wrapping off:
  #Wrapping Apples
  Wrapping_Apples<-0
```

```{r warning=TRUE}
#Running Loop First: 
source("Main_Loops2.R")
```

```{r}

#STEP 1: WAshing, Run model with washing on Wrapping off. 

  #1. Start from here
  Individual_Analysis_Fr<-bind_rows(List_Sens_Fr)
  
  #2. find the dupplicates
  #this step filters replicated based on the ID
  Individual_Analysis_Fr<-Individual_Analysis_Fr %>% 
    group_by(ID) %>% 
    filter(TotServices==max(TotServices))
  
  #3. This created the data frame for items when washed was on
  Individual_Analysis_Fr_Wash<-Individual_Analysis_Fr
  
  #4. Narrowing down to consumed Items for exposure compisons
  Individual_Analysis_Fr_Consumed_W<-Individual_Analysis_Fr_Wash[which(Individual_Analysis_Fr_Wash$Location == "Consumed"),]
  
  #5 Delta Contaminations
  Individual_Analysis_Fr_Consumed_W$DeltaCont<-Individual_Analysis_Fr_Consumed_W$Contamination-Individual_Analysis_Fr_Consumed_W$InContamination

```

Scenario where wrapping is on and washing is off
```{r}
#Inputs and Source Files
# Source Files ------------------------------------------------------------
start_time<-Sys.time()

#Inputs
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

#Changing Inputs for Washing off, Wraaping on. 
  #Washing Between Services
  Wash_Between_Services<-0
  #Wash Selection Table Fruit
  Wash_Selection_YN_Fr<-0
  #Wash Share Table Items
  Wash_ST_YN_Fr<-0
  
#Changing Wrapping off:
  #Wrapping Apples
  Wrapping_Apples<-1
```

```{r}
#Running Loop again:
source("Main_Loops2.R")
```

```{r}
#STEP 2: Turning on Wrapping, Turning off Washing

  #1. Start from here
  Individual_Analysis_Fr<-bind_rows(List_Sens_Fr)
  
  #2. find the dupplicates
  #this step filters replicated based on the ID
  Individual_Analysis_Fr<-Individual_Analysis_Fr %>% 
    group_by(ID) %>% 
    filter(TotServices==max(TotServices))
  
  #3. This one creates the data frame for the wrapped items consumed
  Individual_Analysis_Fr_Wr<-Individual_Analysis_Fr
  
  Individual_Analysis_Fr_Consumed_Wr<-Individual_Analysis_Fr[which(Individual_Analysis_Fr$Location == "Consumed"),]
  
  #4 Delta Contamination
  Individual_Analysis_Fr_Consumed_Wr$DeltaCont<-Individual_Analysis_Fr_Consumed_Wr$ContConsumed-Individual_Analysis_Fr_Consumed_Wr$InContamination

```


#Dose Response Model Wash on

```{r}
#ST ON
Individual_Analysis_Fr_Wash_Copy<-Individual_Analysis_Fr_Wash
#Individual_Analysis_Fr_Wash<-Individual_Analysis_Fr_Wash_Copy

df1<-Individual_Analysis_Fr_Wash_Copy %>% 
  group_by(week) %>% 
  summarize(count=n())
df1$week<-paste("Week",df1$week)



 Individual_Analysis_Fr_Wash<-Individual_Analysis_Fr_Wash%>%
      group_by(ConsumedBy)%>%
      summarise(Contamination = sum(Contamination))

    Individual_Analysis_Fr_Wash$week <- substr(Individual_Analysis_Fr_Wash$ConsumedBy, 1, 3) 
    Individual_Analysis_Fr_Wash$Infection<-as.logical("")
    Individual_Analysis_Fr_Wash$Illness<-as.logical("")
    
#Analysis For weekly Dose Response ON

Reps_DR<-100

List_week_DR<-split(x=Individual_Analysis_Fr_Wash,f=Individual_Analysis_Fr_Wash$week)
lista<-replicate(Reps_DR,lapply(List_week_DR,Func_Rep_DR),simplify = FALSE)
list_Df_Rep<-lapply(lista, Func_List2DF)
list_Df_Rep<-lapply(list_Df_Rep, setNames, c("Infections", "Illness"))
list_Df_Rep<-lapply(list_Df_Rep,bind_rows)
list_Df_Rep<-bind_cols(list_Df_Rep)


df_inf_Week_Wash = list_Df_Rep[,seq(1, ncol(list_Df_Rep), 2) ]
df_ill_Week_Wash = list_Df_Rep[,seq(2, ncol(list_Df_Rep), 2) ]

df_inf_Week_Wash<-as.data.frame(t(df_inf_Week_Wash))
df_ill_Week_Wash<-as.data.frame(t(df_ill_Week_Wash))

rownames(df_inf_Week_Wash)<-paste("Rep",1:Reps_DR)
rownames(df_ill_Week_Wash)<-paste("Rep",1:Reps_DR)
colnames(df_inf_Week_Wash)<-paste("Week",1:Sens_Iterations)
colnames(df_ill_Week_Wash)<-paste("Week",1:Sens_Iterations)    

```

#Dose Response Model Wrapp on

```{r}
#ST ON
Individual_Analysis_Fr_Wr_Copy<-Individual_Analysis_Fr_Wr
#Individual_Analysis_Fr_Wr<-Individual_Analysis_Fr_Wr_Copy

df1<-Individual_Analysis_Fr_Wr_Copy %>% 
  group_by(week) %>% 
  summarize(count=n())
df1$week<-paste("Week",df1$week)



 Individual_Analysis_Fr_Wr<-Individual_Analysis_Fr_Wr%>%
      group_by(ConsumedBy)%>%
      summarise(Contamination = sum(Contamination))

    Individual_Analysis_Fr_Wr$week <- substr(Individual_Analysis_Fr_Wr$ConsumedBy, 1, 3) 
    Individual_Analysis_Fr_Wr$Infection<-as.logical("")
    Individual_Analysis_Fr_Wr$Illness<-as.logical("")
    
#Analysis For weekly Dose Response ON

Reps_DR<-100

List_week_DR<-split(x=Individual_Analysis_Fr_Wr,f=Individual_Analysis_Fr_Wr$week)
lista<-replicate(Reps_DR,lapply(List_week_DR,Func_Rep_DR),simplify = FALSE)
list_Df_Rep<-lapply(lista, Func_List2DF)
list_Df_Rep<-lapply(list_Df_Rep, setNames, c("Infections", "Illness"))
list_Df_Rep<-lapply(list_Df_Rep,bind_rows)
list_Df_Rep<-bind_cols(list_Df_Rep)


df_inf_Week_Wr = list_Df_Rep[,seq(1, ncol(list_Df_Rep), 2) ]
df_ill_Week_Wr = list_Df_Rep[,seq(2, ncol(list_Df_Rep), 2) ]

df_inf_Week_Wr<-as.data.frame(t(df_inf_Week_Wr))
df_ill_Week_Wr<-as.data.frame(t(df_ill_Week_Wr))

rownames(df_inf_Week_Wr)<-paste("Rep",1:Reps_DR)
rownames(df_ill_Week_Wr)<-paste("Rep",1:Reps_DR)
colnames(df_inf_Week_Wr)<-paste("Week",1:Sens_Iterations)
colnames(df_ill_Week_Wr)<-paste("Week",1:Sens_Iterations)    

```

#Individual boxplots washed
```{r}
df_inf_Week_Wash_Box <- melt(df_inf_Week_Wash, measure.var = paste("Week",1:Sens_Iterations))

df_inf_Week_Wash_Box_Prev<-merge(df_inf_Week_Wash_Box, df1, by.x='variable', by.y='week')
df_inf_Week_Wash_Box_Prev$Prev<-df_inf_Week_Wash_Box_Prev$value/df_inf_Week_Wash_Box_Prev$count

ggplot(df_inf_Week_Wash_Box_Prev, aes(x = variable, y = Prev)) + 
  geom_boxplot() + 
  theme_bw()+
  ylab("# Infected Student")+
  xlab("Week #") +
  ggtitle("ST ON: Dose Response 100 replicates, Prevalence of Infected Students by week")+ 
  theme(plot.title = element_text(hjust = 0.5))

df_ill_Week_Wash_Box <- melt(df_ill_Week_Wash, measure.var = paste("Week",1:Sens_Iterations))
df_ill_Week_Wash_Box_Prev<-merge(df_ill_Week_Wash_Box, df1, by.x='variable', by.y='week')
df_ill_Week_Wash_Box_Prev$Prev<-df_ill_Week_Wash_Box_Prev$value/df_ill_Week_Wash_Box_Prev$count

ggplot(df_ill_Week_Wash_Box_Prev, aes(x = variable, y = Prev)) + 
  geom_boxplot() + 
  theme_bw()+
  ylab("Prevalence of Ill Students")+
  xlab("Week #")+
  ggtitle("ST ON: Dose Response 100 replicates, Prevalence of Ill Students by week")+ 
  theme(plot.title = element_text(hjust = 0.5))

```
#Individual Boxplot Wrapped

```{r}
df_inf_Week_Wr_Box <- melt(df_inf_Week_Wr, measure.var = paste("Week",1:Sens_Iterations))

df_inf_Week_Wr_Box_Prev<-merge(df_inf_Week_Wr_Box, df1, by.x='variable', by.y='week')
df_inf_Week_Wr_Box_Prev$Prev<-df_inf_Week_Wr_Box_Prev$value/df_inf_Week_Wr_Box_Prev$count

ggplot(df_inf_Week_Wr_Box_Prev, aes(x = variable, y = Prev)) + 
  geom_boxplot() + 
  theme_bw()+
  ylab("# Infected Student")+
  xlab("Week #") +
  ggtitle("ST ON: Dose Response 100 replicates, Prevalence of Infected Students by week")+ 
  theme(plot.title = element_text(hjust = 0.5))

df_ill_Week_Wr_Box <- melt(df_ill_Week_Wr, measure.var = paste("Week",1:Sens_Iterations))
df_ill_Week_Wr_Box_Prev<-merge(df_ill_Week_Wr_Box, df1, by.x='variable', by.y='week')
df_ill_Week_Wr_Box_Prev$Prev<-df_ill_Week_Wr_Box_Prev$value/df_ill_Week_Wr_Box_Prev$count

ggplot(df_ill_Week_Wr_Box_Prev, aes(x = variable, y = Prev)) + 
  geom_boxplot() + 
  theme_bw()+
  ylab("Prevalence of Ill Students")+
  xlab("Week #")+
  ggtitle("ST ON: Dose Response 100 replicates, Prevalence of Ill Students by week")+ 
  theme(plot.title = element_text(hjust = 0.5))

```

#Boxplot Together
```{r}
#Infected
df_inf_Week_Wash_Box_Prev$Int<-"Wash"
df_inf_Week_Wr_Box_Prev$Int<-"Wrapped"

df_inf_Week_Tog_Box<-bind_rows(df_inf_Week_Wash_Box_Prev,df_inf_Week_Wr_Box_Prev)

ggplot(df_inf_Week_Tog_Box, aes(x = variable, y = Prev, fill=Int)) + 
  geom_boxplot() + 
  theme_bw()+
  ylab("Prevalence of Infected Student")+
  xlab("Week #") +
  ggtitle("ST Status: Compaison Weekly Dose Response Distribution: Prevalence Infected Students")+ 
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill = "ST Status")

#Ill

df_ill_Week_Wash_Box_Prev$Int<-"Wash"
df_ill_Week_Wr_Box_Prev$Int<-"Wrapped"

df_ill_Week_Tog_Box<-bind_rows(df_ill_Week_Wash_Box_Prev,df_ill_Week_Wr_Box_Prev)

Ill_Prev_Comb_WW<-ggplot(df_ill_Week_Tog_Box, aes(x = variable, y = Prev, fill=Int)) + 
  geom_boxplot() + 
  theme_bw()+
  ylab("Prevalence of Ill Students")+
  xlab("Week #") +
  ggtitle("ST Status: Compaison Weekly Dose Response Distribution: Prevalence Ill Students")+ 
  theme(plot.title = element_text(hjust = 0.5))+
  labs(fill = "ST Status")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(filename = "Ill_Prev_CombWW.png", path = "Dose Response",width = 40,height = 10,)
print(Ill_Prev_Comb)

```

#Ribon Together
```{r}


Ribon_Ill_Wr<-df_ill_Week_Wr_Box_Prev%>%
  group_by(variable)%>%
  summarise(PrevMed= median(Prev),Prev975= quantile(Prev,.975),Prev025= quantile(Prev,.025))%>%
  mutate(Type = "Off")

df_ill_Week_Wash_Box_Prev<-df_ill_Week_Wash_Box_Prev[,-2]

Ribon_Ill_Wash<-df_ill_Week_Wash_Box_Prev%>%
  group_by(variable)%>%
  summarise(PrevMed= median(Prev),Prev975= quantile(Prev,.975),Prev025= quantile(Prev,.025))%>%
  mutate(Type = "on")

Ribbon_Ill_DF<-bind_rows(Ribon_Ill_Wr,Ribon_Ill_Wash)

Ribbon_Ill_WW<-ggplot(Ribbon_Ill_DF, aes(x = variable, y = PrevMed, group = Type)) + 
  geom_ribbon(aes(ymin = Prev975, ymax = Prev025, fill=Type), alpha=0.3 )+ 
  geom_point(aes(color = Type))+
  geom_line(aes(color = Type), size = .5) +   
  labs(x = "Week #", y = "Prevalence of Ill Student per Week") +
  scale_fill_manual(name = '2.5th-97.5th Percentile', values = c("dodgerblue1", "tomato4", "seagreen1"))+ 
  scale_color_manual(name = 'Median', values = c("dodgerblue1", "tomato4", "seagreen1"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(filename = "Ribbon_Ill_WW.png", path = "Dose Response",width = 20,height = 7,)

print(Ribbon_Ill)
```

#Comparison of amounts consumed. 
```{r}
ST_Wr_Analysis_Con<-Individual_Analysis_Fr_Wr_Copy
ST_Wash_Analysis_Con<-Individual_Analysis_Fr_Wash_Copy

ST_Wr_Analysis_Con$Type<-"Wrapped"
ST_Wash_Analysis_Con$Type<-"Washed"

ST_Comb_Analysis_Con<-bind_rows(ST_Wr_Analysis_Con,ST_Wash_Analysis_Con)

ggplot(data =ST_Comb_Analysis_Con, aes(x = Type,fill=Location)  )+
  geom_bar()+
  geom_text(stat = "count",aes(label=..count..),position = position_stack(vjust = .5))

```

#Plots Creation for Exposure
```{r}
#Histogram Exposure
ST_Wash_Analysis_Log<-Individual_Analysis_Fr_Wash
ST_Wash_Analysis_Log$Contamination[ST_Wash_Analysis_Log$Contamination==0]<-(.99)
ST_Wash_Analysis_Log$Log<-log10(ST_Wash_Analysis_Log$Contamination)
ST_Wash_Analysis_Log$Category<-""
ST_Wash_Analysis_Log$OnOff<-"Washed"

ST_Wr_Analysis_Log<-Individual_Analysis_Fr_Wr
ST_Wr_Analysis_Log$Contamination[ST_Wr_Analysis_Log$Contamination==0]<-(.99)
ST_Wr_Analysis_Log$Log<-log10(ST_Wr_Analysis_Log$Contamination)
ST_Wr_Analysis_Log$Category<-""
ST_Wr_Analysis_Log$OnOff<-"Wrapped"


Individual_Analysis_Fr_Wash$OnOff<-"Washed"
Individual_Analysis_Fr_Wr$OnOff<-"Wrapped"
WW_Comb_Analysis_Log<-bind_rows(ST_Wash_Analysis_Log,ST_Wr_Analysis_Log)
WW_Comb_Analysis<-bind_rows(Individual_Analysis_Fr_Wash,Individual_Analysis_Fr_Wr)


Wrapped_Histograms_WW<-ggplot(data = WW_Comb_Analysis_Log,aes(x=Log))+
  geom_histogram(colour="black", alpha=.2,bins =15,boundary = -.001)+
  facet_wrap(~ OnOff)+
  scale_x_continuous( )+
  xlab("Contamination log GEC/Item")+
  ylab("Number of Students")+
  ggtitle("Interventions: Contamination distribution Consumed by Students")+ 
  theme(plot.title = element_text(hjust = 0.5))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", vjust=-.2,bins=15, boundary = -.001,size=3)

ggsave(filename = "Wrapped_Histograms_WW.png", path = "Dose Response",width = 10,height = 6,)
print(Wrapped_Histograms_WW)

WW_Comb_Analysis$Contamination<-log10(WW_Comb_Analysis$Contamination)
ggplot(data = WW_Comb_Analysis)+
  geom_boxplot(mapping = aes(x=OnOff, y =Contamination, fill =OnOff),varwidth = TRUE)

```


```{r}


for (i in 1:nrow(ST_Wash_Analysis_Log)){
  Conta<-as.numeric(ST_Wash_Analysis_Log$Contamination[i])
  if(Conta == .99 ){
    ST_Wash_Analysis_Log$Category[i] <-"0"
  } else if(Conta >0 && Conta< 100 ){
    ST_Wash_Analysis_Log$Category[i]  <-"<0 - 99"
  }else if(Conta >= 100 && Conta < 1000 ){
    ST_Wash_Analysis_Log$Category[i]  <-"100 - 999"
  }else if(Conta >=1000 ){
    ST_Wash_Analysis_Log$Category[i]  <-">=1000"
  }
}


PlotOrder<-c("0","<0 - 99","100 - 999",">=1000")

ST_Wash_Analysis_Log %>% 
  count(Category) %>% 
  mutate(perc = n / nrow(ST_Wash_Analysis_Log)) %>%
  slice(match(Category,PlotOrder))-> tips2

tips2$OnOff<-"Washed"

#off

for (i in 1:nrow(ST_Wr_Analysis_Log)){
  Conta<-as.numeric(ST_Wr_Analysis_Log$Contamination[i])
  if(Conta == .99 ){
    ST_Wr_Analysis_Log$Category[i] <-"0"
  } else if(Conta >0 && Conta< 100 ){
    ST_Wr_Analysis_Log$Category[i]  <-"<0 - 99"
  }else if(Conta >= 100 && Conta < 1000 ){
    ST_Wr_Analysis_Log$Category[i]  <-"100 - 999"
  }else if(Conta >=1000 ){
    ST_Wr_Analysis_Log$Category[i]  <-">=1000"
  }
}


PlotOrder<-c("0","<0 - 99","100 - 999",">=1000")

ST_Wr_Analysis_Log %>% 
  count(Category) %>% 
  mutate(perc = n / nrow(ST_Wr_Analysis_Log)) %>%
  slice(match(Category,PlotOrder))-> tips3

tips3$OnOff<-"Wrapped"

tips4<-bind_rows(tips2,tips3)

library("ggrepel")

ggplot(data =tips4, aes(x = OnOff,y=perc, fill=factor(Category, levels=c("0","<0 - 99","100 - 999",">=1000"))))+
  geom_col(width = .2)+
  geom_text_repel(aes(x = OnOff, 
                      y = perc, 
                      label = paste(round(perc*100,2),"%")),nudge_y = -.2, nudge_x = .15, direction = "x")+
  geom_text_repel(aes(x = OnOff, 
                      y = perc, 
                      label = n),nudge_x = -.15,nudge_y = -.2, direction = "x")+
  labs(fill = "Category")+
  scale_x_discrete(expand = c(.5, 0))+
  coord_flip()+
  xlab(label = "Intervention")+
  ylab(label = "")+
    ggtitle("Composition on Exposure of Individual Students (%)")+ 
  theme(plot.title = element_text(hjust = 0.5))

```


#Summary Table
```{r}
N_Student_ContSTWashed<-nrow(Individual_Analysis_Fr_Wash)
N_Student_ContSTWr<-nrow(Individual_Analysis_Fr_Wr)


MeanPRevWash<-mean(df_ill_Week_Wash_Box_Prev$Prev)
PRev975Wash<-quantile(df_ill_Week_Wash_Box_Prev$Prev,.975)
PRev025Wash<-quantile(df_ill_Week_Wash_Box_Prev$Prev,.025)

MeanPRevWr<-mean(df_ill_Week_Wr_Box_Prev$Prev)
PRev975Wr<-quantile(df_ill_Week_Wr_Box_Prev$Prev,.975)
PRev025Wr<-quantile(df_ill_Week_Wr_Box_Prev$Prev,.025)

MeanPRevinfWash<-mean(df_inf_Week_Wash_Box_Prev$Prev)
PRev975infWash<-quantile(df_inf_Week_Wash_Box_Prev$Prev,.975)
PRev025infWash<-quantile(df_inf_Week_Wash_Box_Prev$Prev,.025)

MeanPRevinfWr<-mean(df_inf_Week_Wr_Box_Prev$Prev)
PRev975infWr<-quantile(df_inf_Week_Wr_Box_Prev$Prev,.975)
PRev025infWr<-quantile(df_inf_Week_Wr_Box_Prev$Prev,.025)


Summary_Comparison_WW<-data.frame(
  "Treatment" = c(1:2),
  "Treatment Desc" = c("Baseline:ST Wash", "Baseline: Share Tables Wr"))

Summary_Comparison_WW<-data.frame(
    "Treatment" = c(1:2),
  "Treatment Desc" = c("Baseline:ST Wash", "Baseline: Share Tables Wr"),
  "NWeeks" = Sens_Iterations,
  "Participating Students" = N_Iterations*Service_No* Food_Days*Sens_Iterations,
  "NStudentCosumedFood" = c(N_Student_ContSTWashed,N_Student_ContSTWr),
  "Prevalence Consump" = (Summary_Comparison_WW$NStudentCosumedFood /Summary_Comparison_WW$Participating.Students),
  "0" = c(tips2$perc[4],0)*100 ,
  ">0" = c(tips2$perc[3],0)*100,
  ">100"=c(tips2$perc[2],0)*100,
  ">1000"= c(tips2$perc[1],0)*100,
    "Mean Prevalence Inf" = c(MeanPRevinfWash,MeanPRevinfWr)*100,
  "Top 97.5 Inf"=c(PRev975infWash,PRev975infWr)*100,
  "Bot 025 Inf"=c(PRev025infWash,PRev025infWr)*100,
  "Mean Prevalence Ill" = c(MeanPRevWash,MeanPRevWr)*100,
  "Top 97.5 Ill"=c(PRev975Wash,PRev975Wr)*100,
  "Bot 025 Ill"=c(PRev025Wash,PRev025Wr)*100,
  stringsAsFactors = FALSE
  )






give.n <- function(x){
 return(c(y = median(x)*1.05, label = length(x))) 
# experiment with the multiplier to find the perfect position
}


# plot
ggplot(mtcars, aes(factor(cyl), mpg, label=rownames(mtcars))) +
 geom_boxplot(fill = "grey80", colour = "#3366FF") +
 stat_summary(fun.data = give.n, geom = "text", fun.y = median) 



ggplot(data = df_ill_Week_Tog_Box, aes(x= Int , y = Prev))+
  geom_boxplot() 


```






















Scenario where it both of the interventions are off

```{r}
#Inputs and Source Files
# Source Files ------------------------------------------------------------
start_time<-Sys.time()

#Inputs
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

#Changing Inputs for Washing off, Wraaping on. 
  #Washing Between Services
  Wash_Between_Services<-0
  #Wash Selection Table Fruit
  Wash_Selection_YN_Fr<-0
  #Wash Share Table Items
  Wash_ST_YN_Fr<-0
  
#Changing Wrapping off:
  #Wrapping Apples
  Wrapping_Apples<-0
```

```{r}
#Running Loop again: 
source("Main_Loops2.R")
```

```{r}


#Step 3. Run the scenarios without Wraaping or Washing

  #1. Start from here
  Individual_Analysis_Fr<-bind_rows(List_Sens_Fr)
  
  #2. find the dupplicates
  #this step filters replicated based on the ID
  Individual_Analysis_Fr<-Individual_Analysis_Fr %>% 
    group_by(ID) %>% 
    filter(TotServices==max(TotServices))
  
  #3. This one creates the data frame for the wrapped items consumed
  Individual_Analysis_Fr_Consumed_NoI<-Individual_Analysis_Fr
  
  Individual_Analysis_Fr_Consumed_NoI<-Individual_Analysis_Fr[which(Individual_Analysis_Fr$Location == "Consumed"),]
  
  #4. Delta Contamination
  
  Individual_Analysis_Fr_Consumed_NoI$DeltaCont<-Individual_Analysis_Fr_Consumed_NoI$Contamination-Individual_Analysis_Fr_Consumed_NoI$InContamination

```


Now the summary Part, Creation of graph and figures.

```{r}
#Step 4: Wrap for the DF, in order to have them as the same type

  #1 Creating DF for the DElta Contamination
  IA_Wash<-Individual_Analysis_Fr_Consumed_W[,c(1,18)]
  IA_Cont<-Individual_Analysis_Fr_Consumed_NoI[,c(1,18)]
  IA_Wrapp<-Individual_Analysis_Fr_Consumed_Wr[,c(1,18)]
  IA_Wash$Type<-"Washed"
  IA_Cont$Type<-"No Intervention"
  IA_Wrapp$Type<-"Wrapped"
  
  names(IA_Wrapp)[2]<-"DeltaCont"
  
  IA_All<-bind_rows(IA_Wash,IA_Cont,IA_Wrapp)
  
  #2. Creating Data Frame for Contamination
  IA_Wash_c<-Individual_Analysis_Fr_Consumed_W[,c(1,4)]
  IA_Cont_c<-Individual_Analysis_Fr_Consumed_NoI[,c(1,4)]
  IA_Wrapp_c<-Individual_Analysis_Fr_Consumed_Wr[,c(1,5)]
  
  #Initial
  IA_Wash_Ini<-Individual_Analysis_Fr_Consumed_W[,c(1,8)]
  IA_Cont_Ini<-Individual_Analysis_Fr_Consumed_NoI[,c(1,8)]
  IA_Wrapp_Ini<-Individual_Analysis_Fr_Consumed_Wr[,c(1,8)]

  
  IA_Wash_c$Type<-"Wash"
  IA_Cont_c$Type<-"No Intervention"
  IA_Wrapp_c$Type<-"Wrapped"
  
  #Initial
  IA_Wrapp_Ini$Type<-"Initial Cont Wr"
  IA_Cont_Ini$Type<-"Initial Cont NI"
  IA_Wash_Ini$Type<-"Initial Cont Wash"
  
  names(IA_Wrapp_c)[2]<-"Contamination"
  
  #Initial
  names(IA_Wrapp_Ini)[2]<-"Contamination"
  names(IA_Wash_Ini)[2]<-"Contamination"
  names(IA_Cont_Ini)[2]<-"Contamination"
  
  
  IA_All_c<-bind_rows(IA_Wash_c,IA_Cont_c,IA_Wrapp_c)
  
  IA_All_Ini<-bind_rows(IA_Wrapp_Ini,IA_Wash_Ini,IA_Cont_Ini)
  
  
  #Making 0s into very small values
  IA_All_c[IA_All_c==0]<-(.1)
  
  IA_All_Ini[IA_All_Ini==0]<-(.1)
```

```{r}
  #Making the Contaminations into log Scale, may not be necessary to analyze. 
  IA_All_cLog<-IA_All_c
  IA_All_cLog$Contamination<-log10(IA_All_cLog$Contamination)
  IA_All_cLog00<-IA_All_cLog[which(IA_All_cLog$Contamination > 0),]
  
  #Initial
  IA_All_IniLog<-IA_All_Ini
  IA_All_IniLog$Contamination<-log10(IA_All_IniLog$Contamination)
  IA_All_IniLog00<-IA_All_IniLog[which(IA_All_IniLog$Contamination > 0),]
  
```

```{r}
#Creation of plot with the log scale, density
#Contamination with log
ggplot(data = IA_All_cLog,aes(x=Contamination, fill=Type, linetype=Type))+
  geom_density(colour="black", alpha=.2)+
  scale_x_continuous(n.breaks = 10)+
  xlab("Contamination log GEC/Item")+
  ylab("Density")+
  ggtitle("Density Curves Interventions")+ 
  theme(plot.title = element_text(hjust = 0.5))

ggplot(data = IA_All_cLog,aes(x=Contamination, fill=Type, linetype=Type))+
  geom_histogram(colour="black", alpha=.2)+
  scale_x_continuous(n.breaks = 10)+
  xlab("Contamination log GEC/Item")+
  ylab("Density")+
  ggtitle("Density Curves Interventions")+ 
  theme(plot.title = element_text(hjust = 0.5))
```


```{r}
#Creation of the Boxplots
library(plyr)
  #Funtion for boxplot
  give.n <- function(x){
    return(c(y = median(x)*1.05, label = length(x))) 
    # experiment with the multiplier to find the perfect position
  }

  #function median
  p_meds <- ddply(IA_All_cLog00, .(Type), summarise, median = median(Contamination))

#boxplot Contamination
ggplot(data = IA_All_cLog00,aes( y=Contamination, x=Type))+
  geom_boxplot(aes(fill=Type),varwidth = TRUE)+
  ylab("Contamination Log PFU/Item")+
  xlab("Intervention Type")+
  ggtitle("Boxplot Intervention Comparison")+ 
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(n.breaks = 15)+
  stat_summary(fun.data = give.n, geom = "text", fun = median,vjust = -3)+
  geom_text(data = p_meds, aes(x = Type, y = median, label = median), 
            size = 3, vjust = +1.5, color="blue")
```

```{r}
#Dose Response
Vec_Infected_NI<-c()
Vec_Infected_W<-c()
Vec_Infected_Wr<-c()

Vec_Ill_NI<-c()
Vec_Ill_W<-c()
Vec_Ill_Wr<-c()

detach(package:plyr)
DR_NOI_FR<-(Individual_Analysis_Fr_Consumed_NoI)%>%
  group_by(ConsumedBy)%>%
  summarise(Contamination = sum(Contamination))
DR_NOI_FR$Infection<-as.logical("")
DR_NOI_FR$Illness<-as.logical("")


  #No Intervention

for (i in 1:5){
  #Dose Response. Adding the Dose Response to the Items
DR_NOI_FR<-Func_DR_Infection(DR_NOI_FR)
DR_NOI_FR<-Func_DR_Illness(DR_NOI_FR)

#Number of Items per category
Number_Inf_NI<-sum(DR_NOI_FR$Infection==TRUE)
Vec_Infected_NI<-c(Vec_Infected_NI,Number_Inf_NI)

Number_Ill_NI<-sum(DR_NOI_FR$Illness==TRUE)
Vec_Ill_NI<-c(Vec_Ill_NI,Number_Ill_NI)
}

median(Number_Inf_NI)
mean(Number_Ill_NI)



  #Wrapped

DR_WR_FR<-(Individual_Analysis_Fr_Consumed_Wr)%>%
  group_by(ConsumedBy)%>%
  summarise(Contamination = sum(Contamination))
DR_WR_FR$Infection<-as.logical("")
DR_WR_FR$Illness<-as.logical("")

  #No Intervention
for (i in 1:5){
  #Dose Response. Adding the Dose Response to the Items
DR_WR_FR<-Func_DR_Infection(DR_WR_FR)
DR_WR_FR<-Func_DR_Illness(DR_WR_FR)

#Number of Items per category
Number_Inf_Wr<-sum(DR_WR_FR$Infection==TRUE)
Vec_Infected_Wr<-c(Vec_Infected_Wr,Number_Inf_Wr)

Number_Ill_Wr<-sum(DR_WR_FR$Illness==TRUE)
Vec_Ill_Wr<-c(Vec_Ill_Wr,Number_Ill_Wr)
}

median(Number_Inf_Wr)
mean(Number_Ill_Wr)




  #Washed

DR_W_FR<-(Individual_Analysis_Fr_Consumed_W)%>%
  group_by(ConsumedBy)%>%
  summarise(Contamination = sum(Contamination))
DR_W_FR$Infection<-as.logical("")
DR_W_FR$Illness<-as.logical("")

  #No Intervention
for (i in 1:5){
  #Dose Response. Adding the Dose Response to the Items
DR_W_FR<-Func_DR_Infection(DR_W_FR)
DR_W_FR<-Func_DR_Illness(DR_W_FR)

#Number of Items per category
Number_Inf_W<-sum(DR_WR_FR$Infection==TRUE)
Vec_Infected_W<-c(Vec_Infected_W,Number_Inf_W)

Number_Ill_W<-sum(DR_W_FR$Illness==TRUE)
Vec_Ill_W<-c(Vec_Ill_W,Number_Ill_W)
}

median(Number_Inf_W)
mean(Number_Ill_W)
```

