---
title: "Sens_Analysis_FoodWaste"
author: "Gustavo Reyes"
date: "3/10/2021"
output: html_document
---
1. Probability of Sharing
  -0.1
  -0.5
  -0.9
2. Probability of Eat_ST_YN
  -0.1
  -0.5
  -0.9
3. Probabiliy of Pick_ST_YN
  -0.1
  -0.5
  -0.9
    

Outputs
  %Total Fruit
  %Consumed ST
  %Consumed Servline
  %Discarded
  %Re-Serviced. 




###Setting Working Directory
```{r}

setwd("C:/Users/gareyes3/Documents/GitHub/Share-Table-QMRA/R") 
#setwd("G:/Share Table QMRA/Share-Table-QMRA/R")
```

###Opening Libary and Inputs
```{r}
source("Util_Library.R")
source("Functions_Full_Analysis.R")
source("Util_FunctionFoodWaste.R")
```



#Input 1: 
Probability of Sharing
#Treatment #1 0.1 probabilty of sharing.


```{r}



Input_No<-1
TreatmentNo<-1

AFWT1<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_share_Food<-0.1


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T1_FWS<-bind_rows(List_Sens_Fr)
T1_VectorFW<-Function_FoodWaste(T1_FWS)

AFWT1[1:6,3]<-T1_VectorFW

```


Probability of Sharing
#Treatment #2 0.5 probabilty of sharing.
```{r}



#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_share_Food<-0.5


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T1_FWS<-bind_rows(List_Sens_Fr)
T1_VectorFW<-Function_FoodWaste(T1_FWS)

AFWT1[1:6,4]<-T1_VectorFW

```


Probability of Sharing
#Treatment #3 0.9 probabilty of sharing.
```{r}



#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_share_Food<-0.9


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T1_FWS<-bind_rows(List_Sens_Fr)
T1_VectorFW<-Function_FoodWaste(T1_FWS)

AFWT1[1:6,5]<-T1_VectorFW

```

#Calculating Results. 

```{r}
for (i in 2:nrow(AFWT1)){
  AFWT1[i,3:5] <- AFWT1[i,3:5]/AFWT1[1,3:5]
}


AFWT1$Index <-(AFWT1$Max-AFWT1$Min)/AFWT1$Nominal
AFWT1$Input<-"Pr Sharing Food"

```
------------------------------------------------

#####Input 2

Probability of Eat_ST_YN

#Treatment #1 0.1 probability of eating ST food.


```{r}



Input_No<-2

AFWT2<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_ST_Fr<-0.1


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```


```{r}
T2_FWS<-bind_rows(List_Sens_Fr)
T2_VectorFW<-Function_FoodWaste(T2_FWS)

AFWT2[1:6,3]<-T2_VectorFW

```


#Treatment #2 0.5 probability of eating ST food.

```{r}


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_ST_Fr<-0.5


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```


```{r}
T2_FWS<-bind_rows(List_Sens_Fr)
T2_VectorFW<-Function_FoodWaste(T2_FWS)

AFWT2[1:6,4]<-T2_VectorFW

```

#Treatment #3 0.9 probability of eating ST food. 

```{r}


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_ST_Fr<-0.9


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```


```{r}
T2_FWS<-bind_rows(List_Sens_Fr)
T2_VectorFW<-Function_FoodWaste(T2_FWS)

AFWT2[1:6,5]<-T2_VectorFW

```

#Calculating Results.

```{r}

for (i in 2:nrow(AFWT2)){
  AFWT2[i,3:5] <- AFWT2[i,3:5]/AFWT2[1,3:5]
}

AFWT2$Index <-(AFWT2$Max-AFWT2$Min)/AFWT2$Nominal
AFWT2$Input<-"Pr Eating ST Food"

```

------------------------------------------------


#Input 3: 
Pick_ST_YN
#Treatment #1 0.1 Pick_ST_YN


```{r}

Input_No<-3

AFWT3<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_Pick_ST_Fr<-0.1


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T3_FWS<-bind_rows(List_Sens_Fr)
T3_VectorFW<-Function_FoodWaste(T3_FWS)

AFWT3[1:6,3]<-T3_VectorFW

```


#Treatment #2 0.5 Pick_ST_YN


```{r}


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_Pick_ST_Fr<-0.5


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}


T3_FWS<-bind_rows(List_Sens_Fr)
T3_VectorFW<-Function_FoodWaste(T3_FWS)

AFWT3[1:6,4]<-T3_VectorFW

```

#Treatment #3 0.9 Pick_ST_YN


```{r}


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_Pick_ST_Fr<-0.9


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T3_FWS<-bind_rows(List_Sens_Fr)
T3_VectorFW<-Function_FoodWaste(T3_FWS)

AFWT3[1:6,5]<-T3_VectorFW

```


#Calculating Results.

```{r}

for (i in 2:nrow(AFWT3)){
  AFWT3[i,3:5] <- AFWT3[i,3:5]/AFWT3[1,3:5]
}

AFWT3$Index <-(AFWT3$Max-AFWT3$Min)/AFWT3$Nominal
AFWT3$Input<-"ST Participation"

```



#Graphics


```{r}
#Creating comparisons for all the 5 diffeent Inputs. 

All_AFW<-bind_rows(AFWT1,AFWT2,AFWT3)


ggplot(data=All_AFW, aes(x= Outputs, y =Index, fill= Input))+
  geom_col(position = "dodge")+
  coord_flip()

```

