---
title: "Sens_Analysis_FoodWaste"
author: "Gustavo Reyes"
date: "3/10/2021"
output: html_document
---
1. Probability of Sharing
  -0.1
  -0.5
  -0.9
2. Probability of Eat_ST_YN
  -0.1
  -0.5
  -0.9
3. Probabiliy of Pick_ST_YN
  -0.1
  -0.5
  -0.9
  
4: Pr_Select_Fruit

5: Pr_Eat Fruit selction

Outputs
  %Total Fruit
  %Consumed ST
  %Consumed Servline
  %Discarded
  %Re-Serviced. 




###Setting Working Directory
```{r}

#setwd("C:/Users/gareyes3/Documents/GitHub/Share-Table-QMRA/R") 
setwd("C:/Users/Gustavo Reyes/Documents/GitHubFiles/Share Table QMRA/Share-Table-QMRA/R")
```

###Opening Libary and Inputs
```{r}
source("Util_Library.R")
source("Functions_Full_Analysis.R")
source("Util_FunctionFoodWaste.R")
```



#Input 1: 
Probability of Sharing
#Treatment #1 0.1 probabilty of sharing.


```{r}



Input_No<-1
TreatmentNo<-1

AFWT1<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T1_FWS<-rbind.fill(List_Sens_Fr)
T1_VectorFW<-Function_FoodWaste(T1_FWS)

AFWT1[1:6,3]<-T1_VectorFW

```


Probability of Sharing
#Treatment #2 0.5 probabilty of sharing.
```{r}

#Inputs and Source Files
TreatmentNo<-2

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T1_FWS<-rbind.fill(List_Sens_Fr)
T1_VectorFW<-Function_FoodWaste(T1_FWS)

AFWT1[1:6,4]<-T1_VectorFW

```


Probability of Sharing
#Treatment #3 0.9 probabilty of sharing.
```{r}
#Inputs and Source Files
TreatmentNo<-3

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T1_FWS<-rbind.fill(List_Sens_Fr)
T1_VectorFW<-Function_FoodWaste(T1_FWS)

AFWT1[1:6,5]<-T1_VectorFW

```

#Calculating Results. 

```{r}
for (i in 2:nrow(AFWT1)){
  AFWT1[i,3:5] <- AFWT1[i,3:5]/AFWT1[1,3:5]
}


AFWT1$Index <-(AFWT1$Max-AFWT1$Min)/AFWT1$Nominal
AFWT1$Input<-"Pr Sharing Food"

```
------------------------------------------------

#####Input 2

Probability of Eat_ST_YN

#Treatment #1 0.1 probability of eating ST food.


```{r}

Input_No<-2
TreatmentNo<-4

AFWT2<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```


```{r}
T2_FWS<-rbind.fill(List_Sens_Fr)
T2_VectorFW<-Function_FoodWaste(T2_FWS)

AFWT2[1:6,3]<-T2_VectorFW

```


#Treatment #2 0.5 probability of eating ST food.

```{r}


#Inputs and Source Files
TreatmentNo<-5

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```


```{r}
T2_FWS<-rbind.fill(List_Sens_Fr)
T2_VectorFW<-Function_FoodWaste(T2_FWS)

AFWT2[1:6,4]<-T2_VectorFW

```

#Treatment #3 0.9 probability of eating ST food. 

```{r}


#Inputs and Source Files
TreatmentNo<-6

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```


```{r}
T2_FWS<-rbind.fill(List_Sens_Fr)
T2_VectorFW<-Function_FoodWaste(T2_FWS)

AFWT2[1:6,5]<-T2_VectorFW

```

#Calculating Results.

```{r}

for (i in 2:nrow(AFWT2)){
  AFWT2[i,3:5] <- AFWT2[i,3:5]/AFWT2[1,3:5]
}

AFWT2$Index <-(AFWT2$Max-AFWT2$Min)/AFWT2$Nominal
AFWT2$Input<-"Pr Eating ST Food"

```

------------------------------------------------


#Input 3: 
Pick_ST_YN
#Treatment #1 0.1 Pick_ST_YN


```{r}

Input_No<-3
TreatmentNo<-7

AFWT3<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")


NSA_FW_Analysis <-1
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T3_FWS<-rbind.fill(List_Sens_Fr)
T3_VectorFW<-Function_FoodWaste(T3_FWS)

AFWT3[1:6,3]<-T3_VectorFW

```


#Treatment #2 0.5 Pick_ST_YN


```{r}

TreatmentNo<-8
#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}


T3_FWS<-rbind.fill(List_Sens_Fr)
T3_VectorFW<-Function_FoodWaste(T3_FWS)

AFWT3[1:6,4]<-T3_VectorFW

```

#Treatment #3 0.9 Pick_ST_YN


```{r}


#Inputs and Source Files
TreatmentNo<-9

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

NSA_FW_Analysis <-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T3_FWS<-rbind.fill(List_Sens_Fr)
T3_VectorFW<-Function_FoodWaste(T3_FWS)

AFWT3[1:6,5]<-T3_VectorFW

```


#Calculating Results.

```{r}

for (i in 2:nrow(AFWT3)){
  AFWT3[i,3:5] <- AFWT3[i,3:5]/AFWT3[1,3:5]
}

AFWT3$Index <-(AFWT3$Min-AFWT3$Max)/AFWT3$Nominal
AFWT3$Input<-"ST Participation Rate"

```


#Input 4: Probability of selecting food at the selection table

```{r}

Input_No<-4
TreatmentNo<-10

AFWT4<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_select_Fr<-0.36



```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T4_FWS<-rbind.fill(List_Sens_Fr)
T4_VectorFW<-Function_FoodWaste(T4_FWS)

AFWT4[1:6,3]<-T4_VectorFW

```


#Treatment #2 0.5 Pr_Select_Fr


```{r}


#Inputs and Source Files
TreatmentNo<-11

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_select_Fr<-0.56


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}


T4_FWS<-rbind.fill(List_Sens_Fr)
T4_VectorFW<-Function_FoodWaste(T4_FWS)

AFWT4[1:6,4]<-T4_VectorFW

```

#Treatment #3 0.9 Pr_Select_Fr


```{r}


#Inputs and Source Files
TreatmentNo<-12

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_select_Fr<-0.76


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T4_FWS<-rbind.fill(List_Sens_Fr)
T4_VectorFW<-Function_FoodWaste(T4_FWS)

AFWT4[1:6,5]<-T4_VectorFW

```


#Calculating Results.

```{r}

for (i in 2:nrow(AFWT4)){
  AFWT4[i,3:5] <- AFWT4[i,3:5]/AFWT4[1,3:5]
}

AFWT4$Index <-(AFWT4$Max-AFWT4$Min)/AFWT4$Nominal
AFWT4$Input<-"Pr_Select_Fr"

```


#Input 5: Probability of consuming food after selection

```{r}

Input_No<-5
TreatmentNo<-13

AFWT5<-data.frame(
  "Input"=Input_No,
  "Outputs"= c("TotalFruit","TotalConsumed","TotalDiscarded","TotalReserviced","ConsumedSel", "ConsumedST"),
  "Min"=as.numeric(0),
  "Nominal"=as.numeric(0),
  "Max"=as.numeric(0),
  "Index"="",
  stringsAsFactors = FALSE)


#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_Fr<-0.43



```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T5_FWS<-rbind.fill(List_Sens_Fr)
T5_VectorFW<-Function_FoodWaste(T5_FWS)

AFWT5[1:6,3]<-T5_VectorFW

```


#Treatment #2 0.5 Pr_Eat_Fr


```{r}


#Inputs and Source Files
TreatmentNo<-14

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_Fr<-0.63


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}


T5_FWS<-rbind.fill(List_Sens_Fr)
T5_VectorFW<-Function_FoodWaste(T5_FWS)

AFWT5[1:6,4]<-T5_VectorFW

```

#Treatment #3 0.9 Pr_eat_Fr


```{r}


#Inputs and Source Files
TreatmentNo<-15

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_Fr<-0.83


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
T5_FWS<-rbind.fill(List_Sens_Fr)
T5_VectorFW<-Function_FoodWaste(T5_FWS)

AFWT5[1:6,5]<-T5_VectorFW

```


#Calculating Results.

```{r}

for (i in 2:nrow(AFWT5)){
  AFWT5[i,3:5] <- AFWT5[i,3:5]/AFWT5[1,3:5]
}

AFWT5$Index <-(AFWT5$Max-AFWT5$Min)/AFWT5$Nominal
AFWT5$Input<-"Pr_Eat_Fr"

```


#Graphics


```{r}
#Creating comparisons for all the 5 diffeent Inputs.
labels2=c("Pr_Eat_Fr"="Prob of Consuming Fruit",
                           "Pr_Select_Fr"= "Prob of Selecting Fruit", 
                            "ST Participation Rate"="Prob of Picking ST Item", 
                             "Pr Eating ST Food"= "Prob of Eating Fruit from ST",
                              "Pr Sharing Food"= "Prob of Sharing Fruit to ST")



iris2 <- arrange(transform(iris,
             Species=factor(Species,levels=neworder)),Species)


All_AFW<-rbind.fill(AFWT1,AFWT2,AFWT3,AFWT4,AFWT5)
All_AFW$Index<-as.numeric(All_AFW$Index)

All_AFW<-All_AFW[!grepl("ConsumedST", All_AFW$Outputs),]
All_AFW<-All_AFW[!grepl("ConsumedSel", All_AFW$Outputs),]

Data1 <- subset(All_AFW, Outputs == "TotalConsumed")

neworder<-c("ST Participation Rate","Pr Sharing Food","Pr Eating ST Food","Pr_Select_Fr","Pr_Eat_Fr")

All_AFW2 <- arrange(transform(All_AFW,
             Input=factor(Input,levels=neworder)),Input)

supp.labs <- c("TotalConsumed" = "Total Fruit Consumed", 
               "TotalDiscarded" = "Total Fruit Wasted",
               "TotalFruit" = "Fruit Utilization by School", 
               "TotalReserviced" = "Total Fruit Reserviced")

FoodWasteNSA<-ggplot(data=All_AFW2,  aes(x=Input,y=Index ))+
  geom_col(position = "dodge")+
  coord_flip()+
  facet_wrap(~ Outputs, scales = "free", labeller = labeller(Outputs= supp.labs))+
  scale_x_discrete(labels = labels2)+
  ylab("Sensitivity Index")+
  xlab("Input Name")+
  ggtitle("Sensitivity Analysis: Food Security Inputs")+
  theme(plot.title = element_text(hjust = 0.5))+

ggsave(filename = "FoodWasteNSA.png", plot = FoodWasteNSA,path = "Manuscript Plots", width = 8, height = 6) 


```

