---
title: "Checking other input paramters"
author: "Gustavo Reyes"
date: "3/15/2021"
output: html_document
---


```{r}

#Setting Working Directory-------------------------------------
#setwd("C:/Users/gareyes3/Documents/GitHub/Share-Table-QMRA/R") 
setwd("C:/Users/Gustavo Reyes/Documents/GitHubFiles/Share Table QMRA/Share-Table-QMRA/R")
pathfolder<-"DoseReponse5-14"
```

```{r}
#Opening Libary and Inputs-------------------------------------
source("Util_Library.R")
source("Functions_Full_Analysis.R")
source("Util_FunctionFoodWaste.R")
```


```{r}
DFCheckingInputs<-data.frame(
  "Input" = 1:10,
  "Description" = "",
  "MaxOut" = "",
  "MinOut" = "",
  "NominalOut"= "",
  "Index"="",
  stringsAsFactors = FALSE
)
```



#Log Reducition Wash
#Min Value, No Reduction. 

```{r}
Input_No<-1
TreatmentNo<-1

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Reduction_wash"

#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
NSA_Analysis_Other_Wash<-1
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

#Wash Selection Table Fruit
Wash_Selection_YN_Fr<-1
#Wash Share Table Items
Wash_ST_YN_Fr<-1


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_1<-rbind.fill(List_Sens_Fr)
meanTI1<-Func_NSA_Summary(Trial = "T1")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI1


```

##-2 Log Reduction

```{r}

TreatmentNo<-2



#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
NSA_Analysis_Other_Wash<-1
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")


#Wash Selection Table Fruit
Wash_Selection_YN_Fr<-1
#Wash Share Table Items
Wash_ST_YN_Fr<-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_2<-rbind.fill(List_Sens_Fr)
meanTI2<-Func_NSA_Summary(Trial = "T2")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI2
```


#Max Out (-5 log)

```{r}
TreatmentNo<-3

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
NSA_Analysis_Other_Wash<-1
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")



#Wash Selection Table Fruit
Wash_Selection_YN_Fr<-1
#Wash Share Table Items
Wash_ST_YN_Fr<-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_3<-rbind.fill(List_Sens_Fr)
meanTI3<-Func_NSA_Summary(Trial = "T3")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI3
```

##Wrapping the out

```{r}
SIndexT1_3<-(meanTI3-meanTI1)/meanTI2
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT1_3
```

#Die off sensitivity: 



#Log Reducition from Die-Off
#DieOFF ON 

```{r}
Input_No<-2
TreatmentNo<-4

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Growth_Time"

#Inputs and Source Files



#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Time_ON<-120


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_4<-rbind.fill(List_Sens_Fr)
meanTI4<-Func_NSA_Summary(Trial = "T4")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI4


#Summary DFs for Future.------------------------------------- 

#Creating Data Frame of Consumed Items for all the products
Individual_Analysis_Fr_CopDieoffON<-rbind.fill(List_Sens_Fr)
#Copy of Compiled Data Frame
Individual_Analysis_Fr_DieoffON<-rbind.fill(List_Sens_Fr)

#Data Frame without repeats and Consumed Items
ST_DieoffON_Analysis<-Func_Asys_MainDF(SummaryList = List_Sens_Fr,FoodType = "Fruit")


#ST Die offON-------------------------------------
ST_DieoffON_Analysis_Copy<-ST_DieoffON_Analysis


ST_DieoffON_Analysis<-Func_Asys_ContbyStudent(ST_DieoffON_Analysis)


#Drop NAs
ST_DieoffON_Analysis<- ST_DieoffON_Analysis[!is.na(ST_DieoffON_Analysis$Contamination), ]

#Analysis For weekly Dose Response ON

OutputsDRDieoffON<-Func_DR_Main(AnalysisDF = ST_DieoffON_Analysis, Reps_DR = 100)
df_inf_Week_DieoffON<-OutputsDRDieoffON$df_inf_Week
df_ill_Week_DieoffON<-OutputsDRDieoffON$df_ill_Week


df_ill_Week_DieoffON_Box_Prev<-Func_DF_Prevalence(AnalysisDFCop = ST_DieoffON_Analysis_Copy, df_Ill_Week = df_ill_Week_DieoffON,Intervention = "OFFWr")

```



#DieOFF Normal

```{r}
Input_No<-2
TreatmentNo<-5

#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")



```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_5<-rbind.fill(List_Sens_Fr)
meanTI5<-Func_NSA_Summary(Trial = "T5")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI5


```


#DieOFF Off

```{r}
Input_No<-2
TreatmentNo<-6

#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Growth<-0
Growth_Pre<-0
Growth_Pss<-0

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_6<-rbind.fill(List_Sens_Fr)
meanTI6<-Func_NSA_Summary(Trial = "T6")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI6


```


##Wrapping the out

```{r}
SIndexT4_6<-(meanTI6-meanTI4)/meanTI5
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT4_6
```




#Ill Exclusion 

```{r}
Input_No<-3
TreatmentNo<-7

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Ill Exclusion"

#Inputs and Source Files



#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

  Ill_Avoid_ST<-0
  Pr_Ill_Avoid_ST<-0


```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_7<-rbind.fill(List_Sens_Fr)
meanTI7<-Func_NSA_Summary(Trial = "T7")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI7


```



#Ill Exlusion Normal

```{r}
Input_No<-3
TreatmentNo<-8

#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

  Ill_Avoid_ST<-1
  Pr_Ill_Avoid_ST<-0.5

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_8<-rbind.fill(List_Sens_Fr)
meanTI8<-Func_NSA_Summary(Trial = "T8")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI8


```


#DieOFF Off

```{r}
Input_No<-3
TreatmentNo<-9

#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")


  Ill_Avoid_ST<-1
  Pr_Ill_Avoid_ST<-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_9<-rbind.fill(List_Sens_Fr)
meanTI9<-Func_NSA_Summary(Trial = "T9")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI9


```


##Wrapping the out

```{r}
SIndexT7_9<-(meanTI9-meanTI7)/meanTI8
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT7_9
```





#Hand Sanitizer

```{r}
Input_No<-4
TreatmentNo<-10

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Hand Sanitizer"

#Inputs and Source Files



#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
NSA_Analysis_Other_Sanitize<-1
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Sanitizing_Station<-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_10<-rbind.fill(List_Sens_Fr)
meanTI10<-Func_NSA_Summary(Trial = "T10")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI10


```


```{r}
TreatmentNo<-11

#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
NSA_Analysis_Other_Sanitize<-1
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Sanitizing_Station<-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_11<-rbind.fill(List_Sens_Fr)
meanTI11<-Func_NSA_Summary(Trial = "T11")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI11


```

```{r}
TreatmentNo<-12

#Inputs and Source Files


#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
NSA_Analysis_Other_Sanitize<-1
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Sanitizing_Station<-1

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_12<-rbind.fill(List_Sens_Fr)
meanTI12<-Func_NSA_Summary(Trial = "T12")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI12


```

##Wrapping the out

```{r}
SIndexT10_12<-(meanTI10-meanTI12)/meanTI11
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT10_12
```

##Behavioral Parameters: 

5. Probability of Sharing
  -0.1
  -0.5
  -0.9
6. Probability of Eat_ST_YN
  -0.1
  -0.5
  -0.9
7. Probabiliy of Pick_ST_YN
  -0.1
  -0.5
  -0.9
  
8: Pr_Select_Fruit

9: Pr_Eat Fruit selction

Outputs
  %Total Fruit
  %Consumed ST
  %Consumed Servline
  %Discarded
  %Re-Serviced. 

#Probability of sharing

#Max
```{r}
Input_No<-5
TreatmentNo<-34

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Probability of Sharing"

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_34<-rbind.fill(List_Sens_Fr)
meanTI34<-Func_NSA_Summary(Trial = "T34")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI34
```
#Mode
```{r}
TreatmentNo<-35

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_35<-rbind.fill(List_Sens_Fr)
meanTI35<-Func_NSA_Summary(Trial = "T35")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI35
```

#Min
```{r}
TreatmentNo<-36

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_36<-rbind.fill(List_Sens_Fr)
meanTI36<-Func_NSA_Summary(Trial = "T36")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI36
```

##Wrapping the out treatment 5

```{r}
SIndexT34_36<-(meanTI34-meanTI36)/meanTI35
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT34_36
```



#Probability of Eating ST for YN

#Max
```{r}
Input_No<-6
TreatmentNo<-37

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Probability of Eat ST"

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_37<-rbind.fill(List_Sens_Fr)
meanTI37<-Func_NSA_Summary(Trial = "T37")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI37
```
#Mode
```{r}
TreatmentNo<-38

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_38<-rbind.fill(List_Sens_Fr)
meanTI38<-Func_NSA_Summary(Trial = "T38")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI38
```

#Min
```{r}
TreatmentNo<-39

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_39<-rbind.fill(List_Sens_Fr)
meanTI39<-Func_NSA_Summary(Trial = "T39")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI39
```

##Wrapping the out treatment 6

```{r}
SIndexT37_39<-(meanTI37-meanTI39)/meanTI38
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT37_39
```


#Probabiliy of Pick_ST_YN

#Max
```{r}
Input_No<-7
TreatmentNo<-40

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Probability of Pick ST"

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_40<-rbind.fill(List_Sens_Fr)
meanTI40<-Func_NSA_Summary(Trial = "T40")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI40
```
#Mode
```{r}
TreatmentNo<-41

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_41<-rbind.fill(List_Sens_Fr)
meanTI41<-Func_NSA_Summary(Trial = "T41")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI41
```

#Min
```{r}
TreatmentNo<-42

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")
```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_42<-rbind.fill(List_Sens_Fr)
meanTI42<-Func_NSA_Summary(Trial = "T42")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI42
```

##Wrapping the out treatment 7

```{r}
SIndexT40_42<-(meanTI40-meanTI42)/meanTI41
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT40_42
```


## 8 Probability of selecting food at the selection table

#Max
```{r}
Input_No<-8

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Probability of Pick Selection"

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_select_Fr<-0.76

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_43<-rbind.fill(List_Sens_Fr)
meanTI43<-Func_NSA_Summary(Trial = "T43")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI43
```

#Nominal
```{r}

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_select_Fr<-0.5

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_44<-rbind.fill(List_Sens_Fr)
meanTI44<-Func_NSA_Summary(Trial = "T44")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI44
```

#Min
```{r}

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_select_Fr<-0.36

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_45<-rbind.fill(List_Sens_Fr)
meanTI45<-Func_NSA_Summary(Trial = "T45")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI45
```

##Wrapping the out treatment 8

```{r}
SIndexT45_43<-(meanTI45-meanTI43)/meanTI44
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT45_43
```


## 9 Probability of eating fruit from seL TABLE
#Max
```{r}
Input_No<-9

#Adding it to the DF
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Description"]<-"Probability of Eat Selection"

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_Fr<-0.83

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_46<-rbind.fill(List_Sens_Fr)
meanTI46<-Func_NSA_Summary(Trial = "T46")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MaxOut"]<-meanTI46
```

#Nominal
```{r}

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_eat_Fr<-0.63

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_47<-rbind.fill(List_Sens_Fr)
meanTI47<-Func_NSA_Summary(Trial = "T47")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="NominalOut"]<-meanTI47
```

#Min
```{r}

#Inputs and Source Files

#Inputs
source("New_StudentLoop.R")
source("Input_Static.R")
source("Input_Functions.R")
source("Util_DFFunctions.R")
source("Util_DFWeekCreation.R")
source("Util_Counter&Lists.R")
#Functions
source("Util_Functions.R")
source("Util_CCFunctions2.R")
source("Util_VisualFunctions.R")

Pr_select_Fr<-0.43

```

```{r warning=TRUE}
#Running Loop First:-------------------------------------
start_time<-Sys.time()
source("Main_Loops2.R")
```

```{r}
TI_48<-rbind.fill(List_Sens_Fr)
meanTI48<-Func_NSA_Summary(Trial = "T48")
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="MinOut"]<-meanTI48
```

##Wrapping the out treatment 9

```{r}
SIndexT48_46<-(meanTI48-meanTI46)/meanTI47
DFCheckingInputs[Input_No,colnames(DFCheckingInputs)=="Index"]<-SIndexT48_46
```




#Creation of final analyses

```{r}
DFCheckingInputsx<-DFCheckingInputs[1:9,]
FullSA<-rbind(DFCheckingInputsx,SenstivityDF)

FullSA$Index<-as.numeric(FullSA$Index)
round(FullSA$Index, 3)


description_color<-c("Reduction",
                     "Amplification",
                     "Reduction",
                     "Reduction",
                     "Behavioral",
                     "Behavioral",
                     "Behavioral",
                     "Behavioral",
                     "Behavioral",
                     "Contamination",
                     "Contamination",
                     "Reduction",
                     "Behavioral",
                     "Contamination",
                     "Contamination",
                     "Contamination",
                     "Contamination",
                     "Contamination",
                     "Behavioral",
                     "Reduction")

 Label_v = scale_x_discrete(labels=c("mass_feces_hands"="Mass of Feces Hands",
                           "TrP_H_S"= "Transfer Prob Hand - Surface", 
                            "TrP_H_F"="Transfer Prob Hand - Food", 
                             "TrP_F_H"= "Transfer Prob Food-Hand",
                              "TrP_S_H"= "Transfer Prob Surface-Hand",
                              "Prevalence_Illness"="Illness Prevalence",
                              "N_Touched"="Additional Touches When Choosing Fruit",
                              "LogRedWash"="Hand Washing Efficacy Baseline",
                              "HU_NV_in_Feces"="Norovirus GEC in Feces",
                           "PrWashingHands" = 'Probability of Washing Hands',
                           "Reduction_wash"= "Fruit Wash Efficacy",
                           "Growth_Time"= "Die Off length (h)",
                           "Ill Exclusion" = "% of Ill Students Excluded from Share Table",
                           "Hand Sanitizer" = "Hand Sanitizer Station 100% Compliance",
                            "HanwashingStationEfficacy"= "Hanwashing Station 100% Compliance",
                           "Probability of Sharing" = "Probability of Sharing",
                           "Probability of Eat ST"="Probability of Eat ST",
                           "Probability of Pick ST" = "Probability of Pick ST",
                           "Probability of Pick Selection" = "Probability of Pick Selection",
                           "Probability of Eat Selection" = "Probability of Eat Selection")) 

 FullSA$Input_Category<-description_color
 
install.packages("remotes")
remotes::install_github("coolbutuseless/ggpattern")

library(ggplot2)
library(ggpattern)

 
  TornadoFull<-ggplot(data = FullSA, aes(x=reorder(Description,abs(Index)),y=Index, fill = Input_Category ))+
    geom_bar(stat = "identity", position = "identity")+
    ylab("Sensitivity Index")+
    xlab("Input Name")+
    ggtitle("Nominal Range Sensitivity Analysis: Effect on mean illness prevalence")+
    Label_v +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5, size = 10))+
    scale_y_continuous(n.breaks = 10)+
    scale_fill_grey()+
    labs(fill= "Input Category")
  
  
  ggplot(data = FullSA,aes(x=reorder(Description,abs(Index)),y=Index))+
    geom_col_pattern(aes(pattern = Input_Category, pattern_angle =  Input_Category, pattern_spacing =  Input_Category), 
    fill            = 'white',
    colour          = 'black', 
    pattern_density = 0.2, 
    pattern_fill    = 'black',
    pattern_colour  = 'black'
   )+
    scale_pattern_spacing_discrete(range = c(0.01, 0.02)) + 
    ylab("Sensitivity Index")+
    xlab("Input Name")+
    ggtitle("Nominal Range Sensitivity Analysis: Effect on mean illness prevalence")+
    Label_v +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5, size = 10))+
    scale_y_continuous(n.breaks = 10)+
    scale_color_grey(start = 0.0,end = 0.7)+
    labs(fill= "Input Category")
  
  
  

ggsave(filename = "Tornado1.png", plot = TornadoFull,path = "C:/Users/Gustavo Reyes/Box/Share Table Project/QMRA Files/QMRA Paper/New Journal Draft/Figures", width = 8, height = 6) 
print(TornadoFull)
```



